Quasi-consistent efficient meshfree thin shell formulation with penalty-free essential boundary condition enforcement

### 2024-03-25 response.tex

\textbf{Response:} Authors thank the reviewer for the suggestion. The expression to calcualte rotation ($\boldsymbol \theta$) is derived as follows:
\begin{equation}
    \begin{split}
        \epsilon_{3i} = 0 \Rightarrow &
        \left \{
        \begin{split}
            \boldsymbol \theta \cdot \boldsymbol a_\alpha &= - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \\
            \boldsymbol \theta \cdot \boldsymbol a_3 &= 0
        \end{split}
        \right . \\ \Rightarrow &
        \boldsymbol \theta = \underbrace{\boldsymbol \theta \cdot \boldsymbol a_{\alpha}}_{- \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3} \boldsymbol a^\alpha 
        + \underbrace{\boldsymbol \theta \cdot \boldsymbol a_3}_{0} \boldsymbol a^3 = - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \boldsymbol a^\alpha
    \end{split}
\end{equation}
Based on reveiwers suggestion Eq. (9) on Page 6 (lines 150) has been modified to provide more clarity regarding the calculation of rotation ($\boldsymbol \theta$).

\textbf{Comment 2.} \textit{Consider using different symbols for the mid-surface displacement, v is always referring to velocity.}

\textbf{Response:} Authors appreciate reviewer's suggestion regarding the representation of mid-surface displacement. However, it has to be noted that present research article doesnot deal with the calculation of velocity. Therefore, the authors believe that the use of notation $\boldsymbol v$ to represent mid-surface displacement will not create confusion.

\textbf{Comment 3.} $\boldsymbol \theta$ \textit{is the variation of $\boldsymbol a_3$, so $\boldsymbol \theta \cdot \boldsymbol a_3=0$. This relationship does not come from $\epsilon_{3i} = 0$, which was in Eq. (9).}
% TODO: please check it i have modified it

\textbf{Response:} Authors appreciate the reviewers insight regarding the calculation of ??? (is it strain or what please add the technical term here). In the authors' opinion, the equation $\epsilon_{3i}=0$ is equivalent with $\boldsymbol \theta \cdot \boldsymbol a_3$, which follows the Kirchhoff hypothesis of shear deformation. Previoulsy, Benzaken et al. [4] also adopted similar approach to calculate the rotation.

@@

\textbf{Comment 5.} \textit{Patchtest: table 2 is interesting. Eq. (62) assumes the solution is only polynomials on the mid-surface, which is already not a polynomial in the Cartesian coordinate. The flat model is simple, in this case, the parametric domain is the same as Cartesian. I believe the error in the curved case is due to bad parametrization. In general, the solution should be able to reproduce the parametric polynomials if the integration and parametrization are both good.}
% TODO: please check the technicality related to the polynomial and error
% NOTE: revised
% NOTE: checked and modified
\textbf{Response:} Authors are thankful to the reviewer for the careful insight. In the present study, the proposed approach as given in Eqs. (32, 33, 35, 36) was used to designate polynomial strains and stresses. It can be found from Eqs. (7) and (8), of the revised manuscript the strains were expressed by the in-plane covariant base ($\boldsymbol a_i$) and the derivatives of displacement ($\boldsymbol v_{,i}$). For the flat surface model, both of $\boldsymbol a_i$ and $\boldsymbol v_{,i}$ are polynomials, so the mesh free formulation can easily pass the patch test. However, in the case of the curved surface model, the $\boldsymbol a_i$ turns to be non-polynomial due the parametrization of curvilinear coordinate system. As a result, even though the integration and parametrization are well poised, the approximated smoothed stresses cannot exactly reproduce the non-polynomial stresses. For this reason, the adopted approach in the present study was termed as "quasi-consistent".

@@

\textbf{Response:} Authors are thankful to the reviewer for identifying the grammatical error. The sentence below Eq. (22)  has beeen modified in the revised mansucript on Page 9 as "208". Besides, the manuscript was double checked to address other grammatical and typo issues.

\textbf{Comment 2.} \textit{Why is only the quadratic function used for the basis function vector p in Eq. (23)?}

\textbf{Response:} In the present study, the proposed method is in the context of RKGSI framework that can be easily extended for the high order basis functions. However, for conciseness, only quadratic basis function was considered in this study which can be considered as a limitation. The formulation with high order basis functions will be considered in the further work and the related statements has been added  in the conclusion of the revised manuscript on Page 27.

\textbf{Comment 3.} \textit{Please provide the meaning of the symbol $s_{\alpha I}$ in Eq. (25). What is the parameter value used in this paper?}
% TODO: please check the parameter assignment
% NOTE: add some statements.
% NOTE: modified accordingly.. please check
\textbf{Response:} The parameter $s_{\alpha I}$ represents the support size of the shape function $\Psi_I$. Accordingly, the statements related  to support size has been added on Page 9 (line??). Besides, the authors have also checked the definitions of all the symbols in the revised manuscript. The value of characterized support size of shape function is taken ad 2.5 for all the considered examples, which is reported on Page 20 (line 342).

@@

\textbf{Comment 5.} \textit{On page 13, the authors stated that "Even with p-th order variational consistency, the proposed formulation can not exactly reproduce the solution spanned by basis functions". The reproducibility is important for Galerkin meshfree methods. So, just suggestion, is it possible to give some more explicit explanations.}

\textbf{Response:} The reproducibility is one of the essential requirement for the Galerkin formulation variational consistency to achieve an optimal accuracy. Based on reviewer's suggestion, the discussion related to the reproducibility and consistency conditions were added on Page 2 of the revised manuscript.

\textbf{6.} \textit{Numerical results of Nitsche's method and penalty method are also shown in Section 5.1. The values of penalty parameters used in the two methods should be provided. In addition, it is encouraged to provide some observations on numerical results of the RKGSI-penalty in Figure 4 and Tables 1 and 2.}

\textbf{Reply:} Based on reviewer's suggestion, to provide further clarity the artificial parameters used in Nitsche's method and penalty method were updated on Page 19. Additional discussions for RKGSI-penalty were also added on Pages 19 and 20 of the revised manuscript. 
% WARN:did you modify the figures.. if so please mention that figures were also modified in the revised manuscript. 
% NOTE: I modify the figures, however it is not for the comment, it's for the reviewer 1 's Comment 6 
% NOTE: you can add the modifications here also.. no problem

### 2024-03-26 response.tex

\textbf{Response:} Authors thank the reviewer for the suggestion. The expression to calcualte rotation ($\boldsymbol \theta$) is derived as follows:
\begin{equation}
    \begin{split}
        \epsilon_{3i} = 0 \Rightarrow &
        \left \{
        \begin{split}
            \boldsymbol \theta \cdot \boldsymbol a_\alpha &= - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \\
            \boldsymbol \theta \cdot \boldsymbol a_3 &= 0
        \end{split}
        \right . \\ \Rightarrow &
        \boldsymbol \theta = \underbrace{\boldsymbol \theta \cdot \boldsymbol a_{\alpha}}_{- \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3} \boldsymbol a^\alpha 
        + \underbrace{\boldsymbol \theta \cdot \boldsymbol a_3}_{0} \boldsymbol a^3 = - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \boldsymbol a^\alpha
    \end{split}
\end{equation}
Based on reveiwers suggestion Eq. (9) on Page 6 (lines 150) has been modified to provide more clarity regarding the calculation of rotation ($\boldsymbol \theta$).

\textbf{Comment 2.} \textit{Consider using different symbols for the mid-surface displacement, v is always referring to velocity.}

\textbf{Response:} Authors appreciate reviewer's suggestion regarding the representation of mid-surface displacement. However, it has to be noted that present research article doesnot deal with the calculation of velocity. Therefore, the authors believe that the use of notation $\boldsymbol v$ to represent mid-surface displacement will not create confusion.

\textbf{Comment 3.} $\boldsymbol \theta$ \textit{is the variation of $\boldsymbol a_3$, so $\boldsymbol \theta \cdot \boldsymbol a_3=0$. This relationship does not come from $\epsilon_{3i} = 0$, which was in Eq. (9).}

\textbf{Response:} Authors appreciate the reviewers insight regarding the calculation of rotation ($\boldsymbol \theta$). In the authors' opinion, the equation $\epsilon_{3i}=0$ is equivalent with $\boldsymbol \theta \cdot \boldsymbol a_3$, which follows the Kirchhoff hypothesis of shear deformation. Previoulsy, Benzaken et al. [4] also adopted similar approach to calculate the rotation.

@@

\textbf{Comment 5.} \textit{Patchtest: table 2 is interesting. Eq. (62) assumes the solution is only polynomials on the mid-surface, which is already not a polynomial in the Cartesian coordinate. The flat model is simple, in this case, the parametric domain is the same as Cartesian. I believe the error in the curved case is due to bad parametrization. In general, the solution should be able to reproduce the parametric polynomials if the integration and parametrization are both good.}

\textbf{Response:} Authors are thankful to the reviewer for the careful insight. In the present study, the proposed approach as given in Eqs. (32, 33, 35, 36) was used to designate polynomial strains and stresses. It can be found from Eqs. (7) and (8), of the revised manuscript the strains were expressed by the in-plane covariant base ($\boldsymbol a_i$) and the derivatives of displacement ($\boldsymbol v_{,i}$). For the flat surface model, both of $\boldsymbol a_i$ and $\boldsymbol v_{,i}$ are polynomials, so the meshfree formulation can easily pass the patch test. However, in the case of the curved surface model, the $\boldsymbol a_i$ turns to be non-polynomial due the parametrization of curvilinear coordinate system. As a result, even though the integration and parametrization are well posed, the approximated smoothed stresses cannot exactly reproduce the non-polynomial stresses. For this reason, the adopted approach in the present study was termed as "quasi-consistent".

@@

\textbf{Response:} Authors are thankful to the reviewer for identifying the grammatical error. The sentence below Eq. (22)  has beeen modified in the revised mansucript on Page 9 as "208". Besides, the manuscript was double checked to address other grammatical and typo issues.

\textbf{Comment 2.} \textit{Why is only the quadratic function used for the basis function vector p in Eq. (23)?}

\textbf{Response:} In the present study, the proposed method is in the context of RKGSI framework that can be easily extended for the high order basis functions. However, for conciseness, only quadratic basis function was considered in this study which can be considered as a limitation. The formulation with high order basis functions will be considered in the further work and the related statements has been added  in the conclusion of the revised manuscript on Page 27.

\textbf{Comment 3.} \textit{Please provide the meaning of the symbol $s_{\alpha I}$ in Eq. (25). What is the parameter value used in this paper?}

\textbf{Response:} The parameter $s_{\alpha I}$ represents the support size of the shape function $\Psi_I$. Accordingly, the statements related  to support size has been added on Page 9 (line 210). Besides, the authors have also checked the definitions of all the symbols in the revised manuscript. The value of characterized support size of shape function is taken ad 2.5 for all the considered examples, which is reported on Page 20 (line 342).
